Spin canonical divisors of log stacky curves

### 2015-07-01 stacky_write_up/spin_cring.tex
address abstract todos

\begin{abstract}
  The study of rings of modular forms arising from finite-area
	quotients of the upper-half plane by Fuchsian groups may be
	translated to the study of canonical rings by the classical
	results of Kodaira--Spencer. In particular, this work describes
	generators and relations of spin canonical rings of a stacky
	curve equipped with an arbitrary log (or effective)	divisor in a
	generalization of the classical theorems of Max Noether	and Karl
	Petri. As an application, these results strongly bound the
	generator and relation degrees for the aforementioned rings
	of modular forms of arbitrary integral weight with some insight
	into rings of modular forms of fractional weight.
\end{abstract}

>>>>

\begin{abstract}
  The study of rings of modular forms arising from finite-area
	quotients of the upper-half plane by Fuchsian groups may be
	translated to (log spin) canonical rings by the classical
	results of Kodaira--Spencer. This work describes
	generators and relations of spin canonical rings of a stacky
	curve equipped with an arbitrary log	divisor in a
	generalization of the classical theorems of Max Noether	and Karl
	Petri. As an application, these results tightly bound the
	generator and relation degrees for the aforementioned rings
	of modular forms of arbitrary integral weight.
\end{abstract}
